Time Series Analysis with Bandt \& Pompe Symbolization and a Test for White Noise in the Entropy-Complexity Plane

### 2021-10-25 Reports/JOURNAL - Confidence Regions/IT-ConfidenceRegionsR1.tex
Reinforces the importance of the HC-PCA column

In this section, we compare the performance of our test with that of 
previous analyses that employ the Entropy-Complexity plane.
To this aim, we produced $100$ sequences of length $T = \num[scientific-notation=true]{5 e4}$ for each generator and computed the $p$-value for each $D = \{3, 4, 5, 6\}$.
Previous results are shown in Table~\ref{Tab:Literature}, and ours are in Table~\ref{Tab:LiteratureComparations}.
We grouped our results in those that rejected (R) the null hypothesis and those that did not reject it (NR).

\begin{table}
	\caption{Results of the sequences generated by the main PRNGs in the literature. 
		The sequences have length $T=\num[scientific-notation = true]{5 e4}$.}
	\label{Tab:LiteratureComparations}
	\centering
	\begin{tabular}{cccc}
		\toprule
		Algorithm & 
		\multicolumn{1}{c}{$D$} & 
		$p$-value &
		HC-PCA\\
		\cmidrule(lr){1-1}
		\cmidrule(lr){2-2}
		\cmidrule(lr){3-3}
		\cmidrule(lr){4-4}
		MOT & 3 & 0.305 & NR\\
		& 4 & 0.572 & NR\\ 
		& 5 & 0.455 & NR\\ 
		& 6 & 0.508 & NR\\ 
		\cmidrule(lr){1-4}
		MWC & 3 & 0.501 & NR\\
		& 4 & 0.477 & NR\\ 
		& 5 & 0.496 & NR\\ 
		& 6 & 0.496 & NR\\ 
		\cmidrule(lr){1-4}
		COM & 3 & 0.123 & NR\\
		& 4 & 0.002 & R\\ 
		& 5 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
		& 6 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
		\cmidrule(lr){1-4}
		LEH & 3 & 0.531 & NR\\
		& 4 & 0.515 & NR\\ 
		\bottomrule
	\end{tabular}
	\begin{tabular}{|cccc}
		\toprule
		Algorithm & 
		\multicolumn{1}{c}{$D$} & 
		$p$-value &
		HC-PCA\\
		\cmidrule(lr){1-1}
		\cmidrule(lr){2-2}
		\cmidrule(lr){3-3}
		\cmidrule(lr){4-4}
		LEH & 5 & 0.495 & NR\\ 
		& 6 & 0.501 & NR\\ 
		\cmidrule(lr){1-4}
		fGn & 3 & 0.521 & NR\\
		& 4 & 0.519 & NR\\ 
		& 5 & 0.498 & NR\\ 
		& 6 & 0.470 & NR\\
		\cmidrule(lr){1-4}
		%fBm & 3 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
		%& 4 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
		%& 5 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
		%& 6 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
		%\cmidrule(lr){1-4}
		$f^{-k}$ & 3 & 0.482 & NR\\
		& 4 & 0.520 & NR\\ 
		& 5 & 0.513 & NR\\ 
		& 6 & 0.508 & NR\\
		\cmidrule(lr){1-4}
		LCG & 3 & 0.009 & R\\ 
		& 4 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
		& 5 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
		& 6 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
		\bottomrule
	\end{tabular}
\end{table}

>>>>

In this section, we compare the performance of our test with that of 
previous analyses that employ the Entropy-Complexity plane.
To this aim, we produced $100$ sequences of length $T = \num[scientific-notation=true]{5 e4}$ for each generator and computed the $p$-value for each $D = \{3, 4, 5, 6\}$.
Previous results are shown in Table~\ref{Tab:Literature}, and ours are in Table~\ref{Tab:LiteratureComparations}.
We grouped our results in those that rejected (R) the null hypothesis and those that did not reject it (NR), given the p-value obtained by the HC-PCA test. 
The aim of this experiment is to investigate the robustness of the confidence regions generated by TRWNS in samples from different randomness generators.

\begin{table}
	\caption{Results of the sequences generated by the main PRNGs in the literature. 
		The sequences have length $T=\num[scientific-notation = true]{5 e4}$ and the HC-PCA column presents the test results considering the $\SI{5}{\percent}$ significance level.}
	\label{Tab:LiteratureComparations}
	\centering
	\begin{tabular}{cccc}
		\toprule
		Algorithm & 
		\multicolumn{1}{c}{$D$} & 
		$p$-value &
		HC-PCA\\
		\cmidrule(lr){1-1}
		\cmidrule(lr){2-2}
		\cmidrule(lr){3-3}
		\cmidrule(lr){4-4}
		MOT & 3 & 0.305 & NR\\
		& 4 & 0.572 & NR\\ 
		& 5 & 0.455 & NR\\ 
		& 6 & 0.508 & NR\\ 
		\cmidrule(lr){1-4}
		MWC & 3 & 0.501 & NR\\
		& 4 & 0.477 & NR\\ 
		& 5 & 0.496 & NR\\ 
		& 6 & 0.496 & NR\\ 
		\cmidrule(lr){1-4}
		COM & 3 & 0.123 & NR\\
		& 4 & 0.002 & R\\ 
		& 5 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
		& 6 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
		\cmidrule(lr){1-4}
		LEH & 3 & 0.531 & NR\\
		& 4 & 0.515 & NR\\ 
		\bottomrule
	\end{tabular}
	\begin{tabular}{|cccc}
		\toprule
		Algorithm & 
		\multicolumn{1}{c}{$D$} & 
		$p$-value &
		HC-PCA\\
		\cmidrule(lr){1-1}
		\cmidrule(lr){2-2}
		\cmidrule(lr){3-3}
		\cmidrule(lr){4-4}
		LEH & 5 & 0.495 & NR\\ 
		& 6 & 0.501 & NR\\ 
		\cmidrule(lr){1-4}
		fGn & 3 & 0.521 & NR\\
		& 4 & 0.519 & NR\\ 
		& 5 & 0.498 & NR\\ 
		& 6 & 0.470 & NR\\
		\cmidrule(lr){1-4}
		%fBm & 3 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
		%& 4 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
		%& 5 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
		%& 6 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
		%\cmidrule(lr){1-4}
		$f^{-k}$ & 3 & 0.482 & NR\\
		& 4 & 0.520 & NR\\ 
		& 5 & 0.513 & NR\\ 
		& 6 & 0.508 & NR\\
		\cmidrule(lr){1-4}
		LCG & 3 & 0.009 & R\\ 
		& 4 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
		& 5 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
		& 6 & \num[scientific-notation=true]{1.11 e-16} & R\\ 
		\bottomrule
	\end{tabular}
\end{table}
